cor

### 2023-04-11 code/analysis_code/stats/3_correlation.qmd
added chl to enc data

```{r}
#Blind Oso
bo<-
  bo %>%
  mutate(amm = log10(amm), #Log-transforms data
         din_dip = log10(din_dip),
         doc = log10(doc),
         dust = log10(dust)) %>%
  select(!c(secchi, tn, tdn, don)) #Removes non-parametric data

>>>>

```{r}
#Blind Oso
bo<-
  bo %>%
  mutate(amm = log10(amm), #Log-transforms data
         din_dip = log10(din_dip),
         doc = log10(doc),
         dust = log10(dust),
         chl = log10(chl)) %>%
  select(!c(secchi, tn, tdn, don)) #Removes non-parametric data
